The Astropy Project:

### 2017-10-03 main.tex
Update on Overleaf.

\subsection{Statistics}
% Steve C.: overview, circular stats,
% Jake V.:  Lomb-scargle, Bayesian blocks
% Larry:  sigma clipping, biweight stats
% Ze':  Ripley's K (spatial stats)
major additions to be discussed: lomb-scargle, sigma clipping, bayesian blocks, histograms, also:  robust (biweight) statistics

\subsection{Robust Statistical Estimators}

@@

\subsection{Circular Statistics}
\subsection{Lomb-Scargle Periodograms}
\subsection{Ripley's K Function Estimators}
\subsection{Histogram Binning}

>>>>

\subsection{Statistics}

The \astropypkg\ \package{stats} package provides 
statistical tools that are useful for or specific to 
astronomy and are not found in other \python\ 
statistics packages such as \package{scipy} 
\citep{scipy} or \package{statsmodels} 
\citep{seabold2010statsmodels}.   The 
\package{stats} package contains a range of 
different functionality used by many different 
disciplines in astronomy.   It is not a complete set 
of statistic tools, but rather a still growing 
collection of useful features.

The current review process for contributions to the \package{stats} package includes review of the code, documentation, testing, and scientific merit of the inclusion.  When necessary, scientific reviewers outside of the maintainers will be sought for their input on new pull requests.

In this section, we describe these tools that provide a range of different functionality including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.

% Steve C.: overview, circular stats,
% Jake V.:  Lomb-scargle, Bayesian blocks
% Larry:  sigma clipping, biweight stats
% Ze':  Ripley's K (spatial stats)

\subsubsection{Robust Statistical Estimators}

@@

\subsubsection{Circular Statistics}
%steve
\subsubsection{Lomb-Scargle Periodograms}
%jake
\subsubsection{Ripley's K Function Estimators}
%ze
\subsubsection{Histogram Binning}
%jake
